\section{DreamerV3: Scalable Model-Based Reinforcement Learning}

\subsection{Architecture Overview}
DreamerV3 is a model-based reinforcement learning algorithm designed to master diverse domains with fixed hyperparameters. Unlike model-free methods that learn through direct environment interaction, DreamerV3 learns a world model from past experience and optimizes its behavior entirely within an "imagined" latent space. This approach decouples representation learning from policy optimization, providing significant advantages in sample efficiency and stability.

\subsection{The World Model}
The core of the system is the Recurrent State-Space Model (RSSM), which learns to predict the environment's dynamics. The world model consists of several integrated components:

\begin{itemize}
    \item \textbf{Encoder:} Maps high-dimensional observations $x_t$ (e.g., pixels) into a compact, discrete latent state $z_t$. Using categorical variables allows the model to capture multiple possible futures and prevents gradient collapse.
    \item \textbf{Sequence Model (Dynamics):} A recurrent neural network that predicts the prior distribution of the next latent state $\hat{z}_{t+1}$ based on the current state $z_t$ and the action $a_t$.
    \item \textbf{Decoders (Predictors):} These networks branch off the latent state to predict essential environment signals:
    \begin{itemize}
        \item \textbf{Reward Predictor:} Estimates the immediate reward $r_t$.
        \item \textbf{Continue Predictor:} Predicts a discount factor $\gamma_t \in \{0, 1\}$, indicating if the episode will continue.
        \item \textbf{Observation Decoder:} Reconstructs the original input to ensure the latent space retains relevant spatial information.
    \end{itemize}
\end{itemize}

\subsection{Symlog Predictions and Robustness}
To handle the varying scales of rewards and values across different environments without manual tuning, DreamerV3 utilizes the \textit{symlog} transformation:
\begin{equation}
    \text{symlog}(x) = \text{sgn}(x) \ln(|x| + 1)
\end{equation}
The model predicts symlog-transformed targets, which compresses large magnitudes while remaining linear near zero. This ensures that the loss gradients remain stable even when the environment provides extremely high-variance reward signals.

\subsection{Learning in Imagination}
The behavior is learned by an Actor-Critic framework that operates on trajectories generated by the world model. 

\begin{itemize}
    \item \textbf{Critic (Value Model):} Learns to predict the expected $\lambda$-return from a given latent state. It is trained to regress toward the temporal difference (TD) targets calculated within the imagined rollouts.
    \item \textbf{Actor (Policy):} Learns to select actions that maximize the Critic's value estimates and the predicted rewards. It incorporates an entropy bonus to maintain exploration.
\end{itemize}

\subsection{The Learning Cycle}
DreamerV3 operates in three concurrent phases. First, it interacts with the \textbf{Real Environment} to collect experience, which is stored in a replay buffer. Second, it performs \textbf{Representation Learning}, where it samples batches from the buffer to train the world model components via maximum likelihood. Finally, it performs \textbf{Behavior Learning}, where the actor and critic are updated by "dreaming" forward in the latent space using the frozen world model. This loop allows the agent to learn complex behaviors with minimal real-world samples.