\section{Soft Actor-Critic}
\label{sec:sac}

\subsection{Methodology}

We implement Soft Actor-Critic (SAC)~\cite{haarnoja2018sac} for continuous control from image-based observations. SAC is an off-policy actor-critic algorithm that optimizes a stochastic policy under the maximum entropy reinforcement learning framework, encouraging both high reward and exploration.

\textbf{Architecture.} 
Our model consists of a stochastic actor and a double Q-function critic. Observations are high-dimensional images and are first processed through a convolutional encoder that extracts latent features. 

The actor is parameterized as a Gaussian policy. The encoded features are passed through a multi-layer perceptron (MLP) to produce the mean and log-standard deviation of the action distribution. Actions are sampled using the reparameterization trick and passed through a $\tanh$ squashing function to ensure they lie within valid bounds. A correction term is applied to the log-probability to account for this transformation.

The critic is implemented as a \textbf{double Q-network} to reduce overestimation bias. A shared encoder extracts latent features, which are concatenated with the action and passed through two independent Q-heads, producing $Q_1$ and $Q_2$. During training, the minimum of these estimates is used to compute targets.

\textbf{Replay Buffer.} 
We use a uniform replay buffer with fixed capacity to store transitions $(s, a, r, s', d)$. The buffer is implemented using preallocated tensors and a circular indexing scheme for efficiency. Observations are stored as \texttt{uint8} images and normalized to $[0,1]$ at training time to reduce memory usage.

\textbf{Training Objective.} 
SAC optimizes a soft Bellman objective. The critic is trained by minimizing:
\begin{equation}
\mathcal{L}_Q = \mathbb{E}_{(s,a,r,s') \sim \mathcal{D}} \left[ (Q_i(s,a) - y)^2 \right],
\end{equation}
where the target is:
\begin{equation}
y = r + \gamma (1 - d)\left( \min_j Q_j(s', a') - \alpha \log \pi(a'|s') \right).
\end{equation}

The actor is trained to maximize expected Q-values while encouraging entropy:
\begin{equation}
\mathcal{L}_\pi = \mathbb{E}_{s \sim \mathcal{D}} \left[ \alpha \log \pi(a|s) - \min(Q_1, Q_2)(s,a) \right].
\end{equation}

\textbf{Entropy Temperature.} 
We support both fixed and automatically learned entropy temperature $\alpha$. When enabled, $\alpha$ is optimized via:
\begin{equation}
\mathcal{L}_{\alpha} = -\mathbb{E}_{a \sim \pi} \left[ \alpha (\log \pi(a|s) + \mathcal{H}_{\text{target}}) \right],
\end{equation}
where $\mathcal{H}_{\text{target}}$ is typically set proportional to the action dimension, allowing adaptive control of exploration.

\textbf{Training Procedure.} 
Training follows an off-policy loop with interleaved data collection and updates. Multiple environments are run in parallel to improve sample efficiency. Initially, actions are sampled randomly to populate the replay buffer; afterwards, actions are drawn from the learned policy.

At each iteration, a batch is sampled from the replay buffer, the critic is updated using the soft Bellman target, and the actor is updated using the entropy-regularized objective. Target networks are updated using Polyak averaging:
\begin{equation}
\theta_{\text{target}} \leftarrow \tau \theta + (1 - \tau)\theta_{\text{target}}.
\end{equation}

Gradient clipping is optionally applied for stability, and the number of gradient updates per environment step is configurable.

\textbf{Implementation Details.} 
Observations are normalized to $[0,1]$ during training. The method assumes continuous action spaces, as required by SAC. Training progress is monitored via TensorBoard, and models are periodically checkpointed for reproducibility.